Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-25 manuscript/manuscript.Rmd
mini
discussed the rewards/ep len figure

```{r linear_tuning, fig.cap = "Result of the tuning procedure for the constant mortality strategy. (A) Mean episode reward (averaged over 50 episodes) shown as scatter data, and shaded in gray are two standard deviations around each scatter point. Vertical lines correspond to the optimal constant mortality rate $F^* = 0.036$ (red) and $0.8 F^*=0.0288$ (green). (B) Several constant mortality policies shown for illustrative purposes. Slopes $0.02$, $0.03$, $0.055$ and $0.065$ shown in black; the optimal linear policy $F^*X$ shown in red, while $0.8F^*X$ shown in green.", out.width = "6.5in"}
msy_rewards <- msy |>
  group_by(action, rep) |>
  filter(t == max(t)) |> 
  group_by(action) |>
  summarise(mean_reward = mean(reward),
            sd = sd(reward))

@@

>>>>

```{r linear_tuning, fig.cap = "Result of the tuning procedure for the constant mortality strategy. (A) Mean episode reward (averaged over 50 episodes) shown as scatter data, and shaded in gray are two standard deviations around each scatter point. Vertical lines correspond to the optimal constant mortality rate $F^* = $ TBD (red) and $0.8 F^*=$ TBD (green). (B) Several constant mortality policies shown for illustrative purposes. Slopes $0.02$, $0.03$, $0.055$ and $0.065$ shown in black; the optimal linear policy $F^*X$ shown in red, while $0.8F^*X$ shown in green.", out.width = "6.5in"}
msy_rewards <- msy |>
  group_by(action, rep) |>
  filter(t == max(t)) |> 
  group_by(action) |>
  summarise(mean_reward = mean(reward),
            sd = sd(reward))

@@

This time series is representative of the patterns observed in the data (see App. \ref{app:tbd}).
The episode reward and episode length statistics are shown in Fig. \ref{fig:rew_len_fig}.
There, we highlight two things:
First, that the tendency towards early episode ends is fixed by the conservative approach of fishing at 80% of the optimal mortality rate.
In App. \ref{app:tbd} we discuss a warning about this approach, however: the arbitrarily chosen percentange itself lives on a ‘‘knife's edge.’’
More concretely, choosing a higher percentage, say 90%, can switch the behaviour of the controlled system and give rise to the proliferation of early episode ends.
Second, that while the conservative 80% approach has a stable behavior, it consistently produces smaller harvests than a DRL generated policy.
